---
title: "Perceptual Difficulty - Perceptibility"
#output: rmarkdown::github_document
output:
  html_document: default
  #pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data import, include=FALSE}
library(tidyverse)
theme_set(theme_bw())
source("helpers.R")
library(wesanderson)
wp = wes_palette("FantasticFox1")

df = read.csv("../data/results_merged.csv", header = TRUE)

df = df[ ,!(colnames(df) %in% c("utterance","rt","object"))]
df = separate(df,response,into=c("rt","response"),sep=",")
df$rt <- as.character(gsub("\\[","",df$rt))
df$rt = as.numeric(df$rt)
df$response <- as.character(gsub("\\]","",df$response))
df$response <- as.character(gsub(" ","",df$response))
df$correct_answer <- as.character(gsub("\\]","",df$correct_answer))
df$correct_answer <- as.character(gsub("\\[","",df$correct_answer))

df = df %>%
  filter(slide_number_in_experiment == "experimental_trial") %>%
  mutate(gaveRightAnswer=ifelse(response==correct_answer,1,0)) %>%
  mutate(feature_type=fct_recode(feature_type,"color"="['color']","material"="['material']")) %>%
  mutate(id = row_number())
```
**Stimuli check** 
```{r test, echo=FALSE}
d = df %>%
  group_by(label,feature_type,correct_answer)%>%
  count()

table(d$correct_answer,d$feature_type)
```
**Fastest and slowest response times** 
```{r extremes, echo=FALSE}
head(sort(df$rt),10)
tail(sort(df$rt),10)
```

**Exclusions and RT distribution** 
Response times that are 2.5SD away from the mean are excluded
```{r exclusions, echo=FALSE}
exclude =  df %>%
  mutate(Mean=mean(rt),SD=sd(rt),count=n()) %>%
  mutate(Ulimit=Mean+2.5*SD,Llimit=Mean-2.5*SD) %>%
  mutate(slow=ifelse(rt>Ulimit,"1","0")) %>%
  mutate(fast=ifelse(rt<Llimit,"1","0")) %>%
  select(workerid,label,rt,slow,fast,Mean,SD,Ulimit,Llimit,id) %>%
  filter(slow==1)

exclude

df = df[!(df$id %in% exclude$id),]

ggplot(df, aes(x=rt)) +
  geom_histogram(fill="lightblue")
```
**RTs to color and material features (everything collapsed)** 

```{r collapsed, echo=FALSE}
#color vs material RT for correct and incorrect answers
toplot =  df %>%
  group_by(feature_type,gaveRightAnswer) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=factor(gaveRightAnswer))) +
  geom_bar(stat = "identity", position=position_dodge()) +
  scale_fill_manual(values=wp) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer")
```

**RTs to color and material features (only expected YES cases and CORRECT responses)** 

```{r collapsedyescorrect, echo=FALSE}
toplot =  df %>%
  filter(correct_answer=="'yes'") %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(feature_type) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean)) +
  geom_bar(stat = "identity", position=position_dodge(),fill=wp[2]) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer")
```
**RTs to color and material features (only expected YES cases and INCORRECT responses)** 

```{r collapsedyesincorrect, echo=FALSE}
toplot =  df %>%
  filter(correct_answer=="'yes'") %>%
  filter(gaveRightAnswer=="0") %>%
  group_by(feature_type) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean)) +
  geom_bar(stat = "identity", position=position_dodge(),fill=wp[1]) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer")
```
**By item** 

```{r byitem, echo=FALSE}
toplot =  df %>%
  group_by(item,feature_type,gaveRightAnswer) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=factor(gaveRightAnswer))) +
  geom_bar(stat = "identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  scale_fill_manual(values=wp) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~item)

```
**By item (only expected YES cases and CORRECT responses)** 

```{r byitemyescorrect, echo=FALSE}
toplot =  df %>%
  filter(correct_answer=="'yes'") %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(item,feature_type) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean)) +
  geom_bar(stat = "identity", position=position_dodge(),fill=wp[2]) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~item)

```
**By item (only expected YES cases and INCORRECT responses)** 

```{r byitemyesincorrect, echo=FALSE}
toplot =  df %>%
  filter(correct_answer=="'yes'") %>%
  filter(gaveRightAnswer=="0") %>%
  group_by(item,feature_type) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean)) +
  geom_bar(stat = "identity", position=position_dodge(),fill=wp[1]) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~item)

```

**By image** 
```{r byimage, include=FALSE}
toplot =  df %>%
  group_by(label,feature_type, gaveRightAnswer) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=factor(gaveRightAnswer))) +
  geom_bar(stat = "identity", position=position_dodge()) +
  scale_fill_manual(values=wes_palette(("FantasticFox1"))) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~label, ncol=6,scales="free_y")

ggsave(file="../graphs/by_image.pdf",width=14,height=20)

```
**By image (only expected YES cases and CORRECT responses)**

```{r byimageyes, include=FALSE}
toplot =  df %>%
  filter(correct_answer=="'yes'") %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(label,feature_type,item) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=item)) +
  geom_bar(stat = "identity", position=position_dodge()) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "item") +
  facet_wrap(~label, ncol=6)

ggsave(file="../graphs/by_image_yes_correct.pdf",width=14,height=20)

```
**By image (only expected YES cases and CORRECT responses)** ** 
```{r byimageyesincorrect, include=FALSE}
toplot =  df %>%
  filter(correct_answer=="'yes'") %>%
  filter(gaveRightAnswer=="0") %>%
  group_by(label,feature_type,item) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=item)) +
  geom_bar(stat = "identity", position=position_dodge()) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "item") +
  facet_wrap(~label, ncol=6)

ggsave(file="../graphs/by_image_yes_incorrect.pdf",width=14,height=20)

```



