---
title: "Models for Perceptual Difficulty Paper"
output:
  #html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import, include=FALSE}
library(tidyverse)
library(lme4)
library(languageR)
library(brms)
library(lmerTest)

targets = read.csv("../data/targets.csv") #target selections in the production experiment
pd = read.csv(file="../data/pd_by_rt.csv") #response times to target's features in the perceptual difficulty experiment (in context)
```

# Exp.2
**Mixed effects logistic regression predicting redundant adjective use from fixed effects of redundant property, with random by-subject and by-item intercepts**

going from high difficulty-material redundant(0) to low difficulty-color redundant(1) & no redundancy(0) to redundancy(1) --> should be positive
```{r model1, echo=FALSE}
table(targets$trialType)

#centering trialType (not necessary)
targets = targets %>%
  mutate(trialType = as.factor(trialType)) %>%
  mutate(ctrialType = as.numeric(trialType) - mean(as.numeric(trialType)))

m = glmer(redundant ~ trialType + (1|gameid) + (1|clickedobject), data=targets, family="binomial")
summary(m)
```


# Exp.2 & Exp.3
**Mixed effects linear regression predicting logRT to redundant adjective from fixed effects of redundant property --> to replicate the effect from Exp1**

going from high difficulty(0) to low difficulty = material to color adjectives --> logRT decreases = should be negative

```{r model2, echo=FALSE}
pd_tomerge = pd %>% 
  mutate(redundantAdj = as.character(adjQuestion)) %>%
  mutate(targetName = targetname) %>%
  select(targetName,competitorName,notCompetitorName,redundantAdj,MeanRT) #62 rows (for each context we have RT for both color and material adj)

tomodel = targets %>%
  mutate(redundantAdj = ifelse(trialType=="high_difficulty",as.character(clickedmaterial),as.character(clickedcolor))) %>%
  mutate(redundantAdj = ifelse(redundantAdj == "wood", "wooden", redundantAdj)) %>%
  left_join(pd_tomerge, by=c("targetName","competitorName","notCompetitorName","redundantAdj")) %>%
  mutate(logRT = log(MeanRT)) #%>%
  #select(targetName,competitorName,notCompetitorName,redundantAdj,sufficientAdj) %>% #for stimuli check: 31 unique rows 
  #unique()

m1 = lmer(logRT ~ trialType + (1|gameid), data=tomodel,REML=F)
summary(m1)
```

**Mixed effects logistic regression predicting redundant adjective use from redundant property (color or material), RT to redundant adjective in context and their interaction**

bigger RT = more perceptually difficulty = less redundant adjective use
```{r model3, echo=FALSE}
m2 = glmer(redundant ~ trialType*MeanRT + (1|gameid) + (1|clickedobject), data=tomodel, family="binomial")
summary(m2)
```

**Same model with logRT as predictor**
```{r model4, echo=FALSE}
m3 = glmer(redundant ~ trialType*logRT + (1|gameid) + (1|clickedobject), data=tomodel, family="binomial")
summary(m3)
```

**Model comparison btw models with RT and logRT**
```{r model_comp2, echo=FALSE}
anova(m2,m3)
```

**Same model with perceptual difficulty difference score for each context (difference between RTs to target's sufficient and redundant feature)**
```{r model5, echo=FALSE}
pd_wide = pd %>% 
  mutate(targetName = targetname) %>%
  select(targetName,competitorName,notCompetitorName,featureQuestion,MeanRT) %>%
  spread(featureQuestion,MeanRT) %>%
  rename(color_RT = color) %>%
  rename(material_RT = material)

tomodel = targets %>%
  mutate(redundantAdj = ifelse(trialType=="high_difficulty",as.character(clickedmaterial),as.character(clickedcolor))) %>%
  mutate(redundantAdj = ifelse(redundantAdj == "wood", "wooden", redundantAdj)) %>% 
  mutate(sufficientAdj = ifelse(trialType=="high_difficulty",as.character(clickedcolor),as.character(clickedmaterial))) %>%
  mutate(sufficientAdj = ifelse(sufficientAdj == "wood", "wooden", sufficientAdj)) %>% 
  left_join(pd_wide, by=c("targetName","competitorName","notCompetitorName")) %>%
  mutate(diffPd = ifelse(trialType=="high_difficulty",color_RT-material_RT,material_RT-color_RT))

m4 = glmer(redundant ~ diffPd + (1|gameid) + (1|clickedobject), data=tomodel, family="binomial")
summary(m4)
```

**Model comparison btw models with logRT and perceptual difference score**
```{r model_comp1, echo=FALSE}
anova(m3,m4)
```

