---
title: "Models for Perceptual Difficulty Paper"
output:
  #html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import, include=FALSE}
library(tidyverse)
library(lme4)
library(languageR)
library(brms)
library(lmerTest)
library(performance)

source("allFit.R")

targets = read.csv("../data/targets.csv") #target selections in the production experiment
pd = read.csv(file="../data/pd_by_rt.csv") #response times to target's features in the perceptual difficulty experiment (in context)
```

# Exp.2
**Mixed effects logistic regression predicting redundant adjective use from fixed effects of redundant property, with random by-subject and by-item intercepts**

going from high difficulty-material redundant(0) to low difficulty-color redundant(1) & no redundancy(0) to redundancy(1) --> should be positive
```{r model1, echo=FALSE}
table(targets$trialType)
table(targets$redundant)
table(targets$trialType,targets$redundant)
# table(targets$gameid)
table(targets$targetName) # some targets appear in both high-difficulty and low-difficulty trials
table(targets$clickedobject) # multiple targets have the same object types 

#centering trialType 
targets = targets %>%
  mutate(trialType = as.factor(trialType)) %>%
  mutate(ctrialType = as.numeric(trialType) - mean(as.numeric(trialType)))

m = glmer(redundant ~ ctrialType + (1+ctrialType|gameid) + (1|targetName), data=targets, family="binomial")
summary(m)
```


# Exp.2 & Exp.3
**Mixed effects linear regression predicting logRT to redundant adjective from fixed effects of redundant property --> to replicate the effect from Exp1**

going from high difficulty(0) to low difficulty = material to color adjectives --> logRT decreases = should be negative

```{r model2, echo=FALSE}
pd_tomerge = pd %>% 
  mutate(redundantAdj = as.character(adjQuestion)) %>%
  mutate(targetName = targetname) %>%
  select(targetName,competitorName,notCompetitorName,redundantAdj,MeanRT) #62 rows (for each context we have RT for both color and material adj)

tomodel = targets %>%
  mutate(redundant = as.factor(as.character(redundant))) %>% # make sure that redundancy is stored as factor, not as integer
  mutate(redundantAdj = ifelse(trialType=="high_difficulty",as.character(clickedmaterial),as.character(clickedcolor))) %>%
  mutate(redundantAdj = ifelse(redundantAdj == "wood", "wooden", redundantAdj)) %>%
  left_join(pd_tomerge, by=c("targetName","competitorName","notCompetitorName","redundantAdj")) %>%
  mutate(logRT = log(MeanRT),MeanRT = MeanRT/1000) # JD: get log RT and code raw RTs in seconds instead of ms

# JD: this analysis should be done in exp 3, not here. here you've just imported mean RTs by item. to do this analysis properly you need to do it on the RTs you got from exp 3 directly. part of the reason this won't converge is that there isn't any logRT variability by gameid (because nobody in exp 2 took the experiment that estimated RT, so you're just getting the exact same RT for each object regardless of gameid)
m1 = lmer(logRT ~ ctrialType +  (1+ctrialType|gameid) + (1|targetName), data=tomodel,REML=F) 
summary(m1)
```

**Mixed effects logistic regression predicting redundant adjective use from redundant property (color or material), RT to redundant adjective in context and their interaction**

bigger RT = more perceptually difficulty = less redundant adjective use
```{r model3, echo=FALSE}
tomodel = tomodel %>% 
  mutate(cMeanRT = MeanRT-mean(MeanRT), clogRT = logRT-mean(logRT))

m2 = glmer(redundant ~ ctrialType*cMeanRT + (1+ctrialType|gameid) + (1|targetName), data=tomodel, family="binomial") # JD: i fixed the slopes. you had written "(1+trialType) + (1|gameid)", which doesn't mean anything, and i changed it to "(1+trialType|gameid)", which means "for each gameid add random intercept adjustments and random adjustments to the trialType effect. but i also used centered trial type, since that reduces collinearity".
# the problem that remains: the model can't converge (it does converge when you get rid of the by-gameid slope for tiral type, but that's not the right model) because (i think) it can't separate the variance contributed by the trial type and the mean rt predictor
summary(m2)
```

**Same model with logRT as predictor**
```{r model4, echo=FALSE}
m3 = glmer(redundant ~ ctrialType*clogRT + (1|gameid) +  (1|targetName), data=tomodel, family="binomial",control=glmerControl(optimizer="bobyqa",
                                 optCtrl=list(maxfun=2e5))) 
summary(m3)
check_collinearity(m3) # lots of collinearity -- estimates of trial type and log RT likely off. will have to regress one factor against the other and use residuals predictor

# optimizers: bobyqa (default), Nelder_Mead, nlminbwrap, nloptwrap
# doesn't converge in 10000 evaluations, so run it for longer:
# ss = getME(m3,c("theta","fixef"))
# m3.larger = update(m3,start=ss,control=glmerControl(optCtrl=list(maxfun=2e4)))
# summary(m3.larger)
# 
# # try more optimizers
# aa = allFit(m3)

# the model converges just fine, but only finds that trial type affects redundancy. let's compare to the main-effects-only model:

m4 = glmer(redundant ~ ctrialType + clogRT + (1+ctrialType|gameid) +  (1|targetName), data=tomodel, family="binomial")
summary(m4)

anova(m4,m3) # adding interaction term not justified. let's compare to trial-type-only model

m5 = glmer(redundant ~ ctrialType + (1+ctrialType|gameid) +  (1|targetName), data=tomodel, family="binomial")
summary(m5)
anova(m5,m4) # adding main effect of logRT not justified
```

**Same model with perceptual difficulty difference score for each context (difference between RTs to target's sufficient and redundant feature)**
```{r model5, echo=FALSE}
pd_wide = pd %>% 
  mutate(targetName = targetname) %>%
  select(targetName,competitorName,notCompetitorName,featureQuestion,MeanRT) %>%
  spread(featureQuestion,MeanRT) %>%
  rename(color_RT = color) %>%
  rename(material_RT = material)

tomodel = targets %>%
  mutate(redundantAdj = ifelse(trialType=="high_difficulty",as.character(clickedmaterial),as.character(clickedcolor))) %>%
  mutate(redundantAdj = ifelse(redundantAdj == "wood", "wooden", redundantAdj)) %>% 
  mutate(sufficientAdj = ifelse(trialType=="high_difficulty",as.character(clickedcolor),as.character(clickedmaterial))) %>%
  mutate(sufficientAdj = ifelse(sufficientAdj == "wood", "wooden", sufficientAdj)) %>% 
  left_join(pd_wide, by=c("targetName","competitorName","notCompetitorName")) %>%
  mutate(diffPd = ifelse(trialType=="high_difficulty",color_RT-material_RT,material_RT-color_RT))

m4 = glmer(redundant ~ diffPd + (1+trialType) + (1|gameid) + (1|targetName), data=tomodel, family="binomial")
summary(m4)
```
