---
title: "Perceptual Difficulty - Randomized and Timed Perceptibility"
output: rmarkdown::github_document
#output:
  #html_document: default
  #pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data import, include=FALSE}
library(tidyverse)
theme_set(theme_bw())
source("helpers.R")
library(wesanderson)
wp = wes_palette("FantasticFox1")
wp2 = wes_palette("IsleofDogs1")

df = read.csv("../data/results_merged.csv", header = TRUE)
demo = read.csv("../data/subject_info_merged.csv", header = TRUE)

df = separate(df,response,into=c("rt","response"),sep=",")
df$rt <- as.character(gsub("\\[","",df$rt))
df$response <- as.character(gsub("\\']","",df$response))
df$response <- as.character(gsub("\\'","",df$response))
df$response <- as.character(gsub(" ","",df$response))
df = df %>% rename(feature_matching=correct_answer)

df = df %>%
  filter(slide_number_in_experiment != "bot_check") %>%
  filter(slide_number_in_experiment != "practice_trial") %>%
  droplevels %>%
  mutate(gaveRightAnswer=ifelse(response==feature_matching,1,0)) %>%
  mutate(id = row_number()) %>%
  mutate(response = ifelse(rt=="'Late'","late",response))

#remove late responses
df = df %>%
  filter( rt != "'late'")
df$rt = as.numeric(df$rt)

```

**Stimuli check** 
```{r test, echo=FALSE}
d = df %>%
  group_by(label,feature_type,feature_matching)%>%
  count()

table(d$feature_matching,d$feature_type)

#see count of each condition
d = df %>%
  group_by(speaker_cond,feature_type,feature_matching) %>%
  count()

#View(d)
#
```

**Exclusions**
Participants whose native language is not English are excluded
```{r langexclusions, echo=FALSE}
lang_exclude = demo %>%
  select(workerid, language) %>%
  unique() %>%
  filter(str_detect(language,regex("english", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(language,regex("eng", ignore_case=TRUE),negate=TRUE))

lang_exclude

lang_exclude = lang_exclude %>%
  select(workerid)

df = df[!(df$workerid %in% lang_exclude$workerid),]
```


Participants with accuracy lower than 75% are excluded (11 participants)
```{r accexclusions, echo=FALSE}
toplot =  df %>%
  group_by(workerid) %>%
  summarise(Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer)) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(lowacc=ifelse(Mean<0.75,"1","0"))

h=0.85
ggplot(toplot, aes(x=reorder(workerid,Mean), y=Mean, fill=lowacc)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=h) +
  geom_text(aes(0, h, label=h, vjust=-1, hjust=-0.3)) +
  scale_fill_manual(values=wp2)

exclude = toplot %>%
  filter(lowacc==1)

exclude

df = df[!(df$workerid %in% exclude$workerid),]
```

**Proportion of correct responses**

```{r proportion, echo=FALSE}
toplot =  df %>%
  group_by(feature_type,feature_matching) %>%
  summarise(Median=median(gaveRightAnswer),Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=feature_matching)) +
  geom_bar(stat="identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25, position = position_dodge(.9)) +
  scale_fill_manual(values=wp2) +
  xlab("Feature_type") +
  ylab("Proportion of correct responses")
```

**By item - Proportion of correct responses**

```{r proportionitem, echo=FALSE}
toplot =  df %>%
  group_by(item,feature_type,feature_matching) %>%
  summarise(Median=median(gaveRightAnswer),Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=feature_matching)) +
  geom_bar(stat="identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25, position = position_dodge(.9)) +
  scale_fill_manual(values=wp2) +
  xlab("Feature_type") +
  ylab("Proportion of correct responses") +
  facet_wrap(~item)
```

**By unique item - Proportion of correct responses to matching/not matching features** (plot in graphs/)

```{r proportionuniqueitem, include=FALSE}
toplot =  df %>%
  filter(feature_matching=="no") %>%
  group_by(label,item,feature_type) %>%
  summarise(Median=median(gaveRightAnswer),Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=item)) +
  geom_bar(stat="identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25, position = position_dodge(.9)) +
  #geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=2,size=3) +
  #scale_fill_manual(values=wp2) +
  xlab("Feature_type") +
  ylab("Proportion of correct responses") +
  facet_wrap(~label, ncol=6)

ggsave(file="../graphs/by_image_proportion_notmatching.pdf",width=14,height=20)

```

**RT Distribution**
Late responses removed 
```{r exclusions, echo=FALSE}
df = df %>%
  filter(response != "late")

df$rt = as.numeric(df$rt)

ggplot(df, aes(x=rt)) +
  geom_histogram(fill="lightblue")
```


**RTs to color and material features (everything collapsed)** 

```{r collapsed, echo=FALSE}
toplot =  df %>%
  group_by(feature_type,gaveRightAnswer) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=factor(gaveRightAnswer))) +
  geom_bar(stat = "identity", position=position_dodge()) +
  scale_fill_manual(values=wp) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer")
```

**RTs to color and material features (only correct responses to matching features)** 

```{r collapsedyescorrect, echo=FALSE}
toplot =  df %>%
  filter(feature_matching=="yes") %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(feature_type) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean)) +
  geom_bar(stat = "identity", position=position_dodge(),fill=wp[2]) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer")
```

**RTs to color and material features (only incorrect responses to matching features)** 

```{r collapsedyesincorrect, echo=FALSE}
toplot =  df %>%
  filter(feature_matching=="yes") %>%
  filter(gaveRightAnswer=="0") %>%
  group_by(feature_type) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean)) +
  geom_bar(stat = "identity", position=position_dodge(),fill=wp[1]) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer")
```

**By item** 

```{r byitem, echo=FALSE}
toplot =  df %>%
  group_by(item,feature_type,gaveRightAnswer) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=factor(gaveRightAnswer))) +
  geom_bar(stat = "identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  scale_fill_manual(values=wp) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~item)
```

**By item (only correct responses to matching features)** 

```{r byitemyescorrect, echo=FALSE}
toplot =  df %>%
  filter(feature_matching=="yes") %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(item,feature_type) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean)) +
  geom_bar(stat = "identity", position=position_dodge(),fill=wp[2]) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~item)
```

**By item (only incorrect responses to matching features)** 

```{r byitemyesincorrect, echo=FALSE}
toplot =  df %>%
  filter(feature_matching=="yes") %>%
  filter(gaveRightAnswer=="0") %>%
  group_by(item,feature_type) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean)) +
  geom_bar(stat = "identity", position=position_dodge(),fill=wp[1]) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~item)

```

**By image** (plot in graphs/)

```{r byimage, eval=FALSE, include=FALSE}
toplot =  df %>%
  group_by(label,feature_type, gaveRightAnswer) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=factor(gaveRightAnswer))) +
  geom_bar(stat = "identity", position=position_dodge()) +
  scale_fill_manual(values=wes_palette(("FantasticFox1"))) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~label, ncol=6,scales="free_y")

ggsave(file="../graphs/by_image.pdf",width=14,height=20)

```

**By image (only correct responses to matching features)** (plot in graphs/)

```{r byimageyes, include=FALSE}
toplot =  df %>%
  filter(feature_matching=="yes") %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(label,feature_type,item) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=item)) +
  geom_bar(stat = "identity", position=position_dodge()) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "item") +
  facet_wrap(~label, ncol=6)

ggsave(file="../graphs/by_image_correct_matching.pdf",width=14,height=20)

```

**By image (only incorrect responses to matching features)** (plot in graphs/)

```{r byimageyesincorrect, include=FALSE}
toplot =  df %>%
  filter(feature_matching=="yes") %>%
  filter(gaveRightAnswer=="0") %>%
  group_by(label,feature_type,item) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=feature_type, y=Mean, fill=item)) +
  geom_bar(stat = "identity", position=position_dodge()) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "item") +
  facet_wrap(~label, ncol=6)

ggsave(file="../graphs/by_image_incorrect_matching.pdf",width=14,height=20)

```



