---
title: "Perceptual Difficulty - Randomized and Timed Perceptibility2 (difficulty analysis)"
#output: rmarkdown::github_document
output:
  #html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data import, include=FALSE}
library(tidyverse)
theme_set(theme_bw())
source("helpers.R")
library(wesanderson)
wp = wes_palette("FantasticFox1")
wp2 = wes_palette("IsleofDogs1")

df = read.csv("../data/results_merged.csv", header = TRUE)
demo = read.csv("../data/subject_info_merged.csv", header = TRUE)

df = separate(df,response,into=c("rt","response"),sep=",")
df$rt <- as.character(gsub("\\[","",df$rt))
df$response <- as.character(gsub("\\'","",df$response))
df$response <- as.character(gsub("\\]","",df$response))
df$response <- as.character(gsub(" ","",df$response))
df = df %>% rename(feature_matching=correct_answer)

df$condition = paste(df$feature_type,df$feature_matching)

df$rt = as.character(df$rt)

df = df %>%
  filter(slide_number_in_experiment != "bot_check") %>%
  filter(slide_number_in_experiment != "practice_trial") %>%
  mutate(gaveRightAnswer=ifelse(response==feature_matching,1,0)) %>%
  mutate(id = row_number()) %>%
  droplevels()

df = df %>%
  filter(rt != "'late'")

df$rt = as.numeric(df$rt)

```

**Stimuli check** 
```{r test, echo=FALSE}
d = df %>%
  group_by(label,feature_type,feature_matching)%>%
  count()

table(d$feature_matching,d$feature_type)
```

**Exclusions**
Participants whose native language is not English are excluded
```{r langexclusions, echo=FALSE}
lang_exclude = demo %>%
  select(workerid, language) %>%
  unique() %>%
  filter(str_detect(language,regex("english", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(language,regex("eng", ignore_case=TRUE),negate=TRUE))

lang_exclude

lang_exclude = lang_exclude %>%
  select(workerid)

df = df[!(df$workerid %in% lang_exclude$workerid),]
```

Participants with accuracy lower than 75% are excluded (29 participants)
```{r accexclusions, echo=FALSE}
toplot =  df %>%
  group_by(workerid) %>%
  summarise(Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer)) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(lowacc=ifelse(Mean<0.75,"1","0"))

h=0.85
ggplot(toplot, aes(x=reorder(workerid,Mean), y=Mean, fill=lowacc)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=h) +
  geom_text(aes(0, h, label=h, vjust=-1, hjust=-0.3)) +
  scale_fill_manual(values=wp2)

exclude = toplot %>%
  filter(lowacc==1)

exclude

df = df[!(df$workerid %in% exclude$workerid),]
```

# By response times

**Regardless of response correctness and feature matching**
```{r rtall, echo=FALSE}
df <- na.omit(df)

d = df %>%
  group_by(label, condition) %>%
  summarize(Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  #mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(group="rt")

d = d[order(-d$Mean),]

hd_rt=head(d, 15)
ld_rt=tail(d, 15)

hd_rt
ld_rt
```

**Only correct responses, regardless of feature matching**
```{r rtallcorrect, echo=FALSE}
d = df %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(label, condition) %>%
  summarize(Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  #mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(group="correct_rt")
d = d[order(-d$Mean),]

hd_correct_rt=head(d, 15)
ld_correct_rt=tail(d, 15)

hd_correct_rt
ld_correct_rt
```
**Only correct responses, only matching features**
```{r rtcorrectacceptance, echo=FALSE}
d = df %>%
  filter(gaveRightAnswer=="1") %>%
  filter(feature_matching=="yes") %>%
  group_by(label, condition) %>%
  summarize(Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  #mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(group="correct_matching_rt")
d = d[order(-d$Mean),]

hd_correct_matching_rt=head(d, 15)
ld_correct_matching_rt=tail(d, 15)

hd_correct_matching_rt
ld_correct_matching_rt
```
**Only correct responses, only not matching features**
```{r rtcorrectrejection, echo=FALSE}
d = df %>%
  filter(gaveRightAnswer=="1") %>%
  filter(feature_matching=="no") %>%
  group_by(label, condition) %>%
  summarize(Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  #mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(group="correct_notmatching_rt")
d = d[order(-d$Mean),]

hd_correct_notmatching_rt=head(d, 15)
ld_correct_notmatching_rt=tail(d, 15)

hd_correct_notmatching_rt
ld_correct_notmatching_rt
```

# By error rates

**Regardless of feature matching**
```{r erall, echo=FALSE}
d = df %>%
  group_by(label, condition) %>%
  summarize(Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  #mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(group="er")
d = d[order(d$Mean),]

hd_er=head(d, 15)
ld_er=tail(d, 15)

hd_er
ld_er
```
**Only matching features**
```{r eracception], echo=FALSE}
d = df %>%
  filter(feature_matching=="yes") %>%
  group_by(label, condition) %>%
  summarize(Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  #mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(group="matching_er")
d = d[order(d$Mean),]

hd_matching_er=head(d, 15)
ld_matching_er=tail(d, 15)

hd_matching_er
ld_matching_er
```
**Only not matching features**
```{r errejection, echo=FALSE}
d = df %>%
  filter(feature_matching=="no") %>%
  group_by(label, condition) %>%
  summarize(Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  #mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(group="notmatching_er")
d = d[order(d$Mean),]

hd_notmatching_er=head(d, 15)
ld_notmatching_er=tail(d, 15)

hd_notmatching_er
ld_notmatching_er
```

# Is there overlap?
```{r overlap, echo=FALSE}
# 7 high difficulty groups with 15 rows each = 105 rows
high_difficulty = rbind(hd_rt,hd_correct_rt,hd_correct_matching_rt,hd_correct_notmatching_rt,hd_er,hd_matching_er,hd_notmatching_er)

high_difficulty = high_difficulty[c("label","condition","group")]

high_difficulty = high_difficulty %>%
  group_by(label, condition) %>%
  summarize(count=n()) %>%
  arrange(-count)

print(high_difficulty, n = 1e3)

View(high_difficulty)

###################
low_difficulty = rbind(ld_rt,ld_correct_rt,ld_correct_matching_rt,ld_correct_notmatching_rt,ld_er,ld_matching_er,ld_notmatching_er)

low_difficulty = low_difficulty[c("label","condition","group")]

low_difficulty= low_difficulty %>%
  group_by(label, condition) %>%
  summarise(count=n()) %>%
  arrange(-count)

print(low_difficulty, n = 1e3)
View(low_difficulty)
```
