---
title: "Perception in Context"
output: rmarkdown::github_document
#output:
  #html_document: default
  #pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import, include=FALSE}
library(tidyverse)
library(plyr)
source("helpers.R")
library(wesanderson)
wp = wes_palette("FantasticFox1")
wp2 = wes_palette("IsleofDogs1")
theme_set(theme_bw())

demo = read.csv(file="../data/subject-info-merged.csv")
df = read.csv(file="../data/trials-merged.csv")

df = separate(df,response,into=c("rt","response"),sep=",")
df$rt <- as.numeric(gsub("\\[","",df$rt))

df$response <- as.character(gsub("\\']","",df$response))
df$response <- as.character(gsub("\\'","",df$response))
df$response <- as.character(gsub(" ","",df$response))
df = df %>% mutate(number_matching=correctAnsQuestion)
df$number_matching <- as.character(df$number_matching)

df = df %>%
  mutate(targetname = targetName) %>%
  separate(targetName, c("targetobject","targetmaterial","targetcolor","targetoriginal"), sep="_")

```

**Number of participants tested:**

```{r before_exclusions, echo=FALSE}
length(demo$workerid)
table(demo$proliferate.condition)
```
**Stimuli check:**

```{r stimuli_check, echo=FALSE}
critical = df %>%
  filter(utterance != "bot_check") %>%
  filter(slide_number_in_experiment != "practice_trial") %>%
  mutate(gaveRightAnswer= ifelse(number_matching==response,1,0))

table(critical$number_matching,critical$featureQuestion)

check = critical %>%
  group_by(contextID,condition) %>%
  count()

write.csv(critical,"../data/exp3_all_pd.csv") 
```

**Proportion of correct responses by list**

```{r proportion_list, eval=FALSE, include=FALSE}
toplot =  critical %>%
  group_by(proliferate.condition,featureQuestion) %>%
  summarise(Median=median(gaveRightAnswer),Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=proliferate.condition, y=Mean, fill=featureQuestion)) +
  geom_bar(stat="identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25, position = position_dodge(.9)) +
  geom_text(aes(label=count, y=0),position=position_dodge(width=1),vjust=0,size=3) +  
  scale_fill_manual(values=wp2) +
  xlab("Feature_type") +
  ylab("Proportion of correct responses")

#ggsave(file="../graphs/proportion_by_list.pdf",width=6,height=3)
```


**Exclusions**

Remove responses from non-native speakers: 0 participants
TODO: fix this (for now, all pt are native)
```{r exclusions, echo=FALSE}
#notnative = demo %>% 
#  filter(tolower(demo$language) != "english")  #%>% 
#  select(workerid)
#notnative

#df = df[!(df$workerid %in% notnative$workerid),]
```

Participants with accuracy lower than 75% are excluded: 24 participants
```{r accexclusions, echo=FALSE}
toplot =  critical %>%
  group_by(workerid) %>%
  summarise(Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer)) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(lowacc=ifelse(Mean<0.75,"1","0"))

h=0.85
ggplot(toplot, aes(x=reorder(workerid,Mean), y=Mean, fill=lowacc)) +
  geom_bar(stat="identity") +
  geom_hline(yintercept=h) +
  geom_text(aes(0, h, label=h, vjust=-1, hjust=-0.3)) +
  scale_fill_manual(values=wp2)

exclude = toplot %>%
  filter(lowacc==1)
exclude

critical = critical[!(critical$workerid %in% exclude$workerid),]
```

Responses with RT 2.5SD away from the mean are excluded: 217 responses
```{r rtexclusions, echo=FALSE}
rt_exclude =  critical %>%
  mutate(Mean=mean(rt),SD=sd(rt),count=n()) %>%
  mutate(Ulimit=Mean+2*SD,Llimit=Mean-2.5*SD) %>%
  mutate(slow=ifelse(rt>Ulimit,"1","0")) %>%
  mutate(fast=ifelse(rt<Llimit,"1","0")) %>%
  select(workerid,adjQuestion,condition,rt,slow,Mean,SD,Ulimit) %>%
  filter(slow==1)

length(rt_exclude$workerid)

critical = critical[!(critical$workerid %in% rt_exclude$workerid),]
```
**Response time distribution**

```{r rtdist, echo=FALSE}
ggplot(critical, aes(x=rt)) +
  geom_histogram(fill="lightblue")
```

### Error Rates

**Proportion of correct responses by feature type and number match**

```{r proportion, echo=FALSE}
toplot =  critical %>%
  group_by(featureQuestion,number_matching) %>%
  dplyr::summarize(Median=median(gaveRightAnswer),Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=featureQuestion, y=Mean, fill=number_matching)) +
  geom_bar(stat="identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25, position = position_dodge(.9)) +
  scale_fill_manual(values=wp2) +
  xlab("Feature_type") +
  ylab("Proportion of correct responses")

#ggsave(file="../graphs/proportion.pdf",width=6,height=3)
```
```{r proportion2, echo=FALSE}
toplot =  critical %>%
  group_by(featureQuestion) %>%
  dplyr::summarize(Median=median(gaveRightAnswer),Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

dp_by_item =  critical %>%
  group_by(featureQuestion,targetname) %>%
  dplyr::summarize(Median=median(gaveRightAnswer),Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=featureQuestion, y=Mean, fill=featureQuestion)) +
  geom_bar(stat="identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25, position = position_dodge(.9)) +
  #geom_point(data=dp_by_item, aes(y=Mean),alpha=.2) +
  scale_fill_manual(values=c("#FFC20A","#0C7BDC")) +
  xlab("Feature_type") +
  ylab("Proportion of correct responses") +
  theme(legend.position="none")

ggsave(file="../graphs/proportion_for_paper.png",width=3,height=3)

```

**Proportion of correct responses (by context)**

```{r propbyitem, echo=FALSE}
toplot = critical %>%
  group_by(contextID,featureQuestion,number_matching) %>%
  summarise(Median=median(gaveRightAnswer),Mean=mean(gaveRightAnswer),CILow=ci.low(gaveRightAnswer),CIHigh=ci.high(gaveRightAnswer),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=featureQuestion, y=Mean, fill=number_matching)) +
  geom_bar(stat="identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25, position = position_dodge(.9)) +
  scale_fill_manual(values=wp2) +
  xlab("Feature_type") +
  ylab("Proportion of correct responses") +
  facet_wrap(~contextID)

ggsave(file="../graphs/proportion_byContext.pdf",width=14,height=14)

```

### Response Times

**RTs by feature type, number match and response correctness** 

```{r collapsed, echo=FALSE}
toplot =  critical %>%
  group_by(featureQuestion,gaveRightAnswer,number_matching) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh) %>%
  mutate(number_matching_re=fct_recode(number_matching,"feature matching"="yes", "feature not matching"="no"))

toplot$number_matching_re <- factor(toplot$number_matching_re, levels = c("feature matching","feature not matching"))

ggplot(toplot, aes(x=featureQuestion, y=Mean, fill=factor(gaveRightAnswer))) +
  geom_bar(stat = "identity", position=position_dodge()) +
  scale_fill_manual(values=wp) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  geom_text(aes(label=count, y = 5),position=position_dodge(width=1),vjust=0,size=3) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~number_matching_re)

#ggsave(file="../graphs/responsetime.pdf",width=6,height=3)
```
**RTs by feature type, response correctness and context** 

```{r byitem, echo=FALSE}
toplot =  critical %>%
  group_by(contextID,featureQuestion,gaveRightAnswer) %>%
  summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=featureQuestion, y=Mean, fill=factor(gaveRightAnswer))) +
  geom_bar(stat = "identity", position= position_dodge(.9)) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  scale_fill_manual(values=wp) +
  xlab("Feature type") +
  ylab("Mean RT in msec") +
  labs(fill = "gaveRightAnswer") +
  facet_wrap(~contextID) +
  ylim(0,5000)

ggsave(file="../graphs/responsetime_byContext.pdf",width=14,height=14)
```

### Grouping

Proportion of correct answer(acceptance&rejections) and RT of correct answers
```{r grouping, echo=FALSE}
cr = critical %>%
  select(contextID,targetname,competitorName,notCompetitorName,adjQuestion,targetcolor,targetmaterial) %>%
  unique() %>%
  mutate(targetsFeature=ifelse((adjQuestion==targetcolor)|(adjQuestion==targetmaterial),1, 0)) %>%
  select(contextID,targetname,competitorName,notCompetitorName,adjQuestion,targetsFeature)

gr_prop = critical %>%
  #filter(number_matching=="yes") %>%
  group_by(contextID,adjQuestion) %>%
  summarize(MeanProp=mean(gaveRightAnswer))

gr_rt = critical %>%
  mutate(targetmaterial = ifelse(targetmaterial=="wood","wooden",targetmaterial)) %>%
  mutate(targetsFeature=ifelse((adjQuestion==targetcolor)|(adjQuestion==targetmaterial),1, 0)) %>%
  #filter(number_matching=="yes") %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(contextID,targetname,competitorName,notCompetitorName,adjQuestion,featureQuestion,targetsFeature) %>%
  summarize(MeanRT=mean(rt)) %>%
  filter(targetsFeature==1)

write.csv(gr_rt,"../data/pd_by_rt.csv")

gr = gr_prop %>%
  left_join(gr_rt, by=c("contextID","adjQuestion")) %>%
  left_join(cr, by=c("contextID","adjQuestion"))

gr = arrange(gr, MeanRT, MeanProp)

print(gr)
```

Histogram of response times to color and material adjectives 
```{r density, echo=FALSE}
toplot =  critical %>%
  filter(gaveRightAnswer == "1") %>%
  mutate(logRT=log(rt))

means <- ddply(toplot,"featureQuestion",summarise,grp.mean=mean(rt))
  
ggplot(toplot, aes(x=logRT, fill=featureQuestion)) +
  geom_density(alpha=0.6) +
  geom_vline(data=means,aes(xintercept=log(grp.mean), color=featureQuestion), linetype="dashed", show.legend = F) +
  scale_fill_manual(values=c("#FFC20A","#0C7BDC")) +
  scale_color_manual(values=c("#FFC20A","#0C7BDC")) +
  xlab("Log-transformed response time") +
  labs(fill="Feature type")

ggsave(file="../graphs/exp3_density_logRT.png",width=4,height=2.5)

```
```{r collapsed2, echo=FALSE}
toplot =  critical %>%
  filter(number_matching=="yes") %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(featureQuestion) %>%
  dplyr::summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

dp_by_item =  critical %>%
  filter(number_matching=="yes") %>%
  filter(gaveRightAnswer=="1") %>%
  group_by(featureQuestion,targetname) %>%
  dplyr::summarize(Median=median(rt),Mean=mean(rt),CILow=ci.low(rt),CIHigh=ci.high(rt),count=n()) %>%
  ungroup() %>%
  mutate(YMin=Mean-CILow,YMax=Mean+CIHigh)

ggplot(toplot, aes(x=featureQuestion, y=Mean, fill=featureQuestion)) +
  geom_bar(stat = "identity", position=position_dodge()) +
  geom_errorbar(aes(ymin = YMin, ymax = YMax),width=.2, position=position_dodge((.9))) +
  geom_point(data=dp_by_item, aes(y=Mean),alpha=.2) +
  xlab("Feature type") +
  ylab("Mean response time (ms)") +
  scale_fill_manual(values=c("#FFC20A","#0C7BDC")) +
  theme(legend.position="none")

ggsave(file="../graphs/rt_for_paper_d.png",width=3,height=3)

```




